A Parallel General Purpose Multi-Objective Optimization Framework, with Application To Electron Beam Dynamics

### 2018-09-29 paper/prab.tex
eq fix

A set of default operators, corresponding to a mapping to \texttt{C} math
  functions, is included in the dictionary by default.
This enables an out of source description of optimization problem containing
  only simple math primitives.

@@

The parallelization will be explained and benchmarked in detail in a
  forthcoming publication.
One major disadvantage of the master/slave implementation model is the fast
  saturation of the network links surrounding the master node.
In \cite{bctg:09} authors observe an exponential increase in hot-spot latency
  with increasing number of workers that are attached to one master process.
Clearly, the limiting factor is the number of outgoing links of a node in the
  network topology and already for a few workers the links surrounding a
  master process are subject to congestions.
This effect is amplified further by large message sizes.

To that end we implemented a solution propagation based on rumor networks (see
  e.g.\ \cite{bgps:06,ayss:09}) using only one-sided communication.
This limits the number of messages sent over the already heavily used links
  surrounding the master node and at the same time helps to prevent the use of
  global communication.
Using information about the interconnection network topology and the
  application communication graph the task of assigning roles helps to further
  improve the parallel performance.

@@

The framework contains a wrapper implementing the API mentioned in
  Listing 3 for using \textsc{OPAL} \cite{opal} as the forward solver.
\textsc{OPAL} provides different trackers for cyclotrons and linear
  accelerators with satisfactory parallel performance \cite{akir:09}.
Recently we introduced a reduced envelope model \cite{iabc:12} into
  \textsc{OPAL} reducing time to solution by several orders of magnitude.

@@

%\begin{strip}
	\begin{widetext}
		\begin{align} \label{eqn:bench}
		\text{min} & \left[ 1 - \exp \left( -1 \left(
		\left(x_1 - \frac{1}{\sqrt{3}} \right)^2 +
		\left(x_2 - \frac{1}{\sqrt{3}} \right)^2 +
		\left(x_3 - \frac{1}{\sqrt{3}} \right)^2 \right)\right), \right. \\
		\vspace{3em} 
		& \left. 1 - \exp \left( -1 \left(
		\left(x_1 + \frac{1}{\sqrt{3}} \right)^2 +
		\left(x_2 + \frac{1}{\sqrt{3}} \right)^2 +
		\left(x_3 + \frac{1}{\sqrt{3}} \right)^2 \right)\right) \right]^T \nonumber \\
		\vspace{3em} \\
		\text{s.t.} \quad & \quad -1 \le x_i \le 1, \quad i=1,2,3 \nonumber
		\text{.}
		\end{align}
	\end{widetext}
%\end{strip}

>>>>

A set of default operators, corresponding to a mapping to \texttt{C} math
  functions, is included in the dictionary by default.
This enables an out of source description of optimization problems containing
  only simple math primitives.

@@

One major disadvantage of the master/slave implementation model is the fast
  saturation of the network links surrounding the master node.
In \cite{bctg:09} authors observe an exponential increase in hot-spot latency
  with increasing number of workers that are attached to one master process.
Clearly, the limiting factor is the number of outgoing links of a node in the
  network topology and already for a few workers the links surrounding a
  master process are subject to congestions.
This effect is amplified further by large message sizes.

To that end we implemented a solution propagation based on rumor networks 
(see \cite{bgps:06,ayss:09}) using only one-sided communication.
This limits the number of messages sent over the already heavily used links
  surrounding the master node and at the same time helps to prevent the use of
  global communication.
Using information about the interconnection network topology and the
  application communication graph the task of assigning roles helps to further
  improve the parallel performance.

@@

The framework contains a wrapper implementing the API mentioned in
  Listing 3 for using \textsc{OPAL} \cite{opal} as the forward solver.
\textsc{OPAL} provides different trackers for cyclotrons and linear
  accelerators with satisfactory parallel performance \cite{akir:09}.

@@

%\begin{strip}
	\begin{widetext}
		\begin{align} \label{eqn:bench}
		\text{min} & \left[ 1 - \exp \left( -1 \left(
		\left(x_1 - \frac{1}{\sqrt{3}} \right)^2 +
		\left(x_2 - \frac{1}{\sqrt{3}} \right)^2 +
		\left(x_3 - \frac{1}{\sqrt{3}} \right)^2 \right)\right), \right. \\
		\vspace{3em} 
		& \left. 1 - \exp \left( -1 \left(
		\left(x_1 + \frac{1}{\sqrt{3}} \right)^2 +
		\left(x_2 + \frac{1}{\sqrt{3}} \right)^2 +
		\left(x_3 + \frac{1}{\sqrt{3}} \right)^2 \right)\right) \right]^T \nonumber \\
		\vspace{3em} \nonumber \\
		\text{s.t.} \quad & \quad -1 \le x_i \le 1, \quad i=1,2,3 \nonumber
		\text{.} \nonumber
		\end{align}
	\end{widetext}
%\end{strip}
